\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-02 paper.tex
added Maybe monad to improve the plus parser

     With this modification, some deterministic behaviour has been inserted in the \textbf{plus} parser.

>>>>

     \noindent With this modification, some deterministic behaviour has been inserted in the \textbf{plus} parser thus by fixing the sketchy behavior that was being manifested before. \\ \\
     Another way to customize the \textbf{plus} parser is by utilizing the Maybe monad. The following snippet of Haskell code shows how the Just and Nothing constructors can be integrated in the \textbf{plus} parser:

     \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
        p +++ q = \input -> case p input of
                              Just (val, input') -> Just (val, input')
                                         Nothing -> q input
    \end{lstlisting}
    \end{tcolorbox}
